Predicting Solid State Material Platforms for Quantum Technologies

### 2021-12-18 paper.tex
Updates from Overleaf

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{physics}
\usepackage{lipsum}
% \usepackage{subfig} %not compatible with subcaption
% \usepackage{braket}
\usepackage{siunitx}
\usepackage{color}
% \usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz,pgfplots}
\usepackage{makecell}
\captionsetup[table]{skip=10pt}
\pgfplotsset{compat=1.17}
\sisetup{separate-uncertainty}
\usepackage{hyperref} 
% \usepackage{longtable}

@@

\begin{figure}%[h] %!tbp
    \centering
    \begin{subfigure}{1\textwidth}
        \centering
        %\includegraphics[width=1\textwidth]{figures/histograms/01-02-histogram-.pdf}
        \input{figures/histograms/summary-01-02-histogram-.tex}
    \end{subfigure}%

    \begin{subfigure}{1\textwidth}
        \centering
        %\includegraphics[width=1\textwidth]{figures/histograms/03-histogram-.pdf}
        \input{figures/histograms/summary-03-histogram-.tex}
    \end{subfigure}
    \caption{Histograms of predicted materials as a function of band gaps, where all models in an approach agree with at least the probability of $50\%$. The number of predicted materials are $6804$ for the Ferrenti approach, $9227$ for the augmented Ferrenti approach, and $214$ for the intuitive approach.}
    \label{fig:histogram}
\end{figure}

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{physics}
\usepackage{lipsum}
% \usepackage{subfig} %not compatible with subcaption
% \usepackage{braket}
\usepackage{siunitx}
\usepackage{color}
% \usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz,pgfplots}
\usepgfplotslibrary{groupplots,dateplot}
\usetikzlibrary{patterns,shapes.arrows}
\usepackage{makecell}
\captionsetup[table]{skip=10pt}
\pgfplotsset{compat=1.17}
\sisetup{separate-uncertainty}
\usepackage{hyperref} 
% \usepackage{longtable}

@@

\begin{figure}%[h] %!tbp
    \centering
    \begin{subfigure}{1\textwidth}
        \centering
        %\includegraphics[width=1\textwidth]{figures/histograms/01-02-histogram-.pdf}
        \input{figures/histograms/summary-01-02-03-histogram-bg.tex}
        \subcaption[]{}
    \end{subfigure}%

    \begin{subfigure}{1\textwidth}
        \centering
        %\includegraphics[width=1\textwidth]{figures/histograms/03-histogram-.pdf}
        \input{figures/histograms/summary-01-02-03-histogram-cov.tex}
        \subcaption[]{}
    \end{subfigure}

    \begin{subfigure}{1\textwidth}
        \centering
        %\includegraphics[width=1\textwidth]{figures/histograms/03-histogram-.pdf}
        \input{figures/histograms/summary-01-02-03-histogram-ionic.tex}
        \subcaption[]{}
    \end{subfigure}

    \caption{Histograms of predicted suitable materials as a function of (a) PBE-calculated band gap from Materials Project, (b) covalent range (Cov range) and (c) maximum ionic character (Ionic char). The number of predicted materials are $6804$ for the Ferrenti approach, $9227$ for the augmented Ferrenti approach, and $214$ for the intuitive approach.}
    \label{fig:histogram}
\end{figure}
